---
title: "Report about forestry levels over time"
author: "Yuchi Hsieh"
date: "2019/3/1"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
library("ggplot2")
```

### This report focuses on data visualizations of global forestry levels over time. It presents the changing trend of average world-wide forested areas, the relationship between CO2 and forest area and the change in forest area levels for each country.

### Summary visualizations
This graph shows the change of global forested areas over 14 years(1992 to 2016).
Average forested area is calculated by the mean of all countries' data. This graph 
clearly shows that there's a downward trend in average forested area although there's
a small increase from 2015 to 2016. 

```{r line chart of average forested area, echo=FALSE}
ggplot(data = world_forest) +
  geom_path(mapping = aes(x = Year, y = average_global_forest_area, group = 1)) +
  scale_x_discrete(breaks = seq(1992, 2016, 4)) +
  labs(
    title = "Average amount of forested areas world-wide over 14 years",
    y = "Average forested area (% of land area)"
  )
```

Graphs below are intended to find out the relationship between **forest area**
(% of land area) and **CO2 emissions** (metric tons per capita). Data are presented at
a **four-year** interval(six facets). I calculated the average global CO2 emissions (the 
**mean** of world CO2 emissions from 1992 to 2014) by the data in World Bank to group
all countries into two categorical variables which are **"over"** and **"equal or below the average"**. We can learn from this graph that there is **no clear relationship** between forest area and CO2 emissions for countries that have **lower CO2 level** but for countries that 
have **higher level of CO2**, there is **a weak negative relationship**. That is,
forest area correlates to  CO2 emissions for some extent.

```{r scatterplots between forest area and CO2 emissions, echo=FALSE}
ggplot(data = co2_forest) +
  geom_point(mapping = aes(x = `Forest area (% of land area)`, y = 
                             `CO2 emissions (metric tons per capita)`,
                           color = co2_over_average),
             na.rm = T) +
  facet_wrap(~Year) +
  labs(
    title  = "Forest area versus CO2 emissions",
    x = "Forest area (% of land area)",
    y = "CO2 emissions (metric tons per capita)",
    color = "CO2 level"
  )
```

### Map showing changes of forest area
The map below shows the **forestry changes** for each country from 1992 to 2016.
We can see from the map that most countries from Africa and South America have lost 
forest area slightly while most of the countries from Asia and Europe and US have gained
forest area about 1-10 percent. Also, **a country from Africa** have had the **biggest lost**
of forested area.

```{r map of forestes area changes, echo=FALSE}
ggplot(world_shape) +
  geom_polygon(
    mapping = aes(x = long, y = lat, group = group, fill = Loss.level),
    color = "white",
    size = .1
  ) +
  coord_fixed(ratio = 1.6) +
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Global change of forest area from 1992 to 2016",
       fill = "Change of forest area(% of land area)") 
```

### Reference

- CO2 emissions(metric tons per capita), The World Bank, [link](https://data.worldbank.org/indicator/EN.ATM.CO2E.PC?end=2014&start=1992)

